
\begin{thebibliography}{00}
	
	\bibitem{zeinab2017internet} Zeinab, Kamal Aldein Mohammed, and Sayed Ali Ahmed Elmustafa. "Internet of Things applications, challenges and related future technologies." World Scientific News 2.67 (2017): 126-148.
	
	\bibitem{rusitschka2010smart} Rusitschka, S., Eger, K. and Gerdes, C., 2010, October. Smart grid data cloud: A model for utilizing cloud computing in the smart grid domain. In Smart Grid Communications (SmartGridComm), 2010 First IEEE International Conference on (pp. 483-488). IEEE.
	
	\bibitem{mr2017data} MR, M.S., 2017. Data Mining for Internet of Things. International Journal of Current Trends in Science and Technology, 7(12), pp.20556-20560.
	
	\bibitem{owen2012mahout} Owen, Sean, and Sean Owen. "Mahout in action." (2012).
	
	\bibitem{bifet2010moa} Bifet, Albert, Geoff Holmes, Richard Kirkby, and Bernhard Pfahringer. "Moa: Massive online analysis." Journal of Machine Learning Research 11, no. May (2010): 1601-1604.
	
	\bibitem{team2013r} Team, R. Core. "R: A language and environment for statistical computing." (2013): 201.
	
	\bibitem{verleysen2005curse} Verleysen, Michel, and Damien François. "The curse of dimensionality in data mining and time series prediction." In International Work-Conference on Artificial Neural Networks, pp. 758-770. Springer, Berlin, Heidelberg, 2005.
	
	\bibitem{irvingdbscan} Cordova, Irving, and Teng-Sheng Moh. "Dbscan on resilient distributed datasets." In High Performance Computing \& Simulation (HPCS), 2015 International Conference on, pp. 531-540. IEEE, 2015.
	
	\bibitem{zaharia2016apache} Zaharia, Matei, Reynold S. Xin, Patrick Wendell, Tathagata Das, Michael Armbrust, Ankur Dave, Xiangrui Meng et al. "Apache spark: a unified engine for big data processing." Communications of the ACM 59, no. 11 (2016): 56-65.
	
	\bibitem{al2014accelerated} Al-Neama, Mohammed W., Naglaa M. Reda, and Fayed FM Ghaleb. "Accelerated guide trees construction for multiple sequence alignment." International Journal of Advanced Research 2, no. 4 (2014): 14-22.
	
	\bibitem{meng2016mllib} Meng, Xiangrui, Joseph Bradley, Burak Yavuz, Evan Sparks, Shivaram Venkataraman, Davies Liu, Jeremy Freeman et al. "Mllib: Machine learning in apache spark." The Journal of Machine Learning Research 17, no. 1 (2016): 1235-1241.
	
	\bibitem{ahmed2010empirical} Ahmed, Nesreen K., Amir F. Atiya, Neamat El Gayar, and Hisham El-Shishiny. "An empirical comparison of machine learning models for time series forecasting." Econometric Reviews 29, no. 5-6 (2010): 594-621.
	
	\bibitem{kalpakis2001distance} Kalpakis, Konstantinos, Dhiral Gada, and Vasundhara Puttagunta. "Distance measures for effective clustering of ARIMA time-series." In Data Mining, 2001. ICDM 2001, Proceedings IEEE International Conference on, pp. 273-280. IEEE, 2001.
	
	\bibitem{aghabozorgi2015time} Aghabozorgi, Saeed, Ali Seyed Shirkhorshidi, and Teh Ying Wah. "Time-series clustering–A decade review." Information Systems 53 (2015): 16-38.
	
	\bibitem{montero2014tsclust} Montero, Pablo, and José A. Vilar. "Tsclust: An r package for time series clustering." Journal of Statistical Software 62, no. 1 (2014): 1-43.
	
	\bibitem{gubbi2013internet} Gubbi, Jayavardhana, Rajkumar Buyya, Slaven Marusic, and Marimuthu Palaniswami. "Internet of Things (IoT): A vision, architectural elements, and future directions." Future generation computer systems 29, no. 7 (2013): 1645-1660.
	
	\bibitem{alsheikh2014machine} Alsheikh, Mohammad Abu, Shaowei Lin, Dusit Niyato, and Hwee-Pink Tan. "Machine learning in wireless sensor networks: Algorithms, strategies, and applications." IEEE Communications Surveys \& Tutorials 16, no. 4 (2014): 1996-2018.
	
	\bibitem{khan2012future} Khan, Rafiullah, Sarmad Ullah Khan, Rifaqat Zaheer, and Shahid Khan. "Future internet: the internet of things architecture, possible applications and key challenges." In Frontiers of Information Technology (FIT), 2012 10th International Conference on, pp. 257-260. IEEE, 2012.
	
	\bibitem{chen2012challenges} Chen, Yen-Kuang. "Challenges and opportunities of internet of things." In Design Automation Conference (ASP-DAC), 2012 17th Asia and South Pacific, pp. 383-388. IEEE, 2012.
	
	\bibitem{bandyopadhyay2011internet} Bandyopadhyay, Debasis, and Jaydip Sen. "Internet of things: Applications and challenges in technology and standardization." Wireless Personal Communications 58, no. 1 (2011): 49-69.
	
	\bibitem{earley2015analytics} Earley, Seth. "Analytics, machine learning, and the internet of things." IT Professional 17, no. 1 (2015): 10-13.
	
	\bibitem{salvador2007} Salvador, S., and P. Chan. "Fastdtw: Toward accurate dynamic time." Warping in Linear Time and Space (2007).
	
	\bibitem{breeze} Hall, D., and D. Ramage. "Breeze: numerical processing library for Scala." (2009).

	\bibitem{dbscan} Ester, Martin, Hans-Peter Kriegel, Jörg Sander, and Xiaowei Xu. "A density-based algorithm for discovering clusters in large spatial databases with noise." In Kdd, vol. 96, no. 34, pp. 226-231. 1996.
	
	\bibitem{samoa} Morales, Gianmarco De Francisci, and Albert Bifet. "SAMOA: scalable advanced massive online analysis." Journal of Machine Learning Research 16, no. 1 (2015): 149-153.
	
	\bibitem{fastvectorizeddm} Al-Neama, Mohammed W., Naglaa M. Reda, and Fayed FM Ghaleb. "Fast vectorized distance matrix computation for multiple sequence alignment on multi-cores." International Journal of Biomathematics 8, no. 06 (2015): 1550084.
	
\end{thebibliography}

